---
title: "Homework 3"
output: github_document
---

```{r setup}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(dplyr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
First, we need to load the `instacart` data. 

```{r}
data("instacart")
```

The `instacart` data has `r ncol(instacart)` variables and `r nrow(instacart)` observations. The variables include `r names(instacart)`. Among these, eval_set, product_name, aisle, and department are character variables, and the others are numerical variables. 

### How many aisles are there, and which aisles are the most items ordered from?

```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs))
```

There are `134` aisles. The most items ordered form the `fresh vegetables` aisle, and the number of orders from this aisle is 150609. 

### Plotting the number of items ordered in each aisle with more than 10000 items ordered. 

```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs)) %>% 
  filter(n_obs > 10000) %>% 
  ggplot(aes(x = aisle, y = n_obs)) +
  geom_point() +
  labs(
    title = "The Number of Items Ordered in Each Aisle", 
    x = "Aisles", 
    y = "The number of items ordered"
  ) + 
  theme(axis.text.x = element_text(angle = 50, hjust = 1))
```

The scatter plot shows the number of items order in each aisle, which these aisles are those has more than 10000 items ordered. 

### The three most popular items in “baking ingredients”, “dog food care”, and “packaged vegetables fruits”

```{r}
baking = instacart %>% 
  filter(aisle %in% "baking ingredients") %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  arrange(desc(n)) %>% 
  filter(rank <= 3) 

dog = instacart %>% 
  filter(aisle %in% "dog food care") %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  arrange(desc(n)) %>% 
  filter(rank <= 3) 

veg = instacart %>% 
  filter(aisle %in% "packaged vegetables fruits") %>% 
  group_by(aisle) %>%
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  arrange(desc(n)) %>% 
  filter(rank <= 3) 

baking_dog_veg = bind_rows(baking, dog, veg) %>% 
  subset(select = -rank) %>% 
  knitr::kable()
```

The table shows that for `baking ingredients`, the top three popular items are `light brown sugar`, `pure baking soda`, and `cane sugar`, and the corresponding times of order are 499, 387, and 336; for `dog food care` aisle, the top three popular items are `Snack Sticks Chicken & Rice Recipe Dog Treats`, `Organix Chicken & Brown Rice Recipe`, and `Small Dog Biscuits`, and the corresponding times of order are 30, 28, and 26; for `packaged vegetables fruits` aisle, the top three popular items are `organic baby spinach`, `organic raspberries`, and `organic blueberries`, and their corresponding times of order are 9784, 5546, and 4966. 

### The mean hour at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week

```{r}
mean_hours = 
  instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_order_hour = mean(order_hour_of_day)) %>% 
  mutate(order_dow = recode(order_dow, `0` = "Sunday", `1` = "Monday", `2` = "Tuesday", `3` = "Wednesday", `4` = "Thurday", `5` = "Friday", `6` = "Saturday")) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_order_hour
  ) %>% 
  knitr::kable()
```

The table shows that on Sundays, the mean hour of ordering is 13.44118 for pink lady apples and 13.77419 for coffee ice cream; on Mondays, the mean hour is 11.36000 for apples and 14.31579 for ice cream; on Tuesdays, the mean hours are 11.70213 and 15.38095 correspondingly; on Wednesdays, the mean hours are 14.25000 and 15.31818 correspondingly; on Thursdays, the mean hours are 11.55172 and 15.21739 correspondingly; on Fridays, the mean hours are 12.78431 and 12.26316 correspondingly; on Saturdays, the mean hours are 11.93750 and 13.83333 correspondingly. 

# Problem 2

```{r}
data("brfss_smart2010")
```

##Cleaning the data

```{r, message = FALSE}
brfss = 
  brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health", response %in% c("Excellent","Very good","Good","Fair","Poor")) %>% 
  mutate(
    response = ordered(response, levels = c("Poor", "Fair", "Good", "Very good", "Excellent"))
  )
```

### In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r, message = FALSE}
location_2002 = 
  brfss %>% 
  filter(year == "2002") %>% 
  group_by(locationabbr, locationdesc) %>% 
  summarize(n = n()) %>% 
  count(locationabbr) %>% 
  filter(n >= 7)

location_2010 = 
  brfss %>% 
  filter(year == "2010") %>% 
  group_by(locationabbr, locationdesc) %>% 
  summarize(n = n()) %>% 
  count(locationabbr) %>% 
  filter(n >= 7)
```

In 2002, `r pull(location_2002, locationabbr)` were observed at 7 or more locations; in 2010, `r pull(location_2010, locationabbr)` were observed at 7 or more location. 
