---
title: "Homework 3"
output: github_document
---

```{r setup}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(dplyr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
First, we need to load the `instacart` data. 

```{r}
data("instacart")
```

The `instacart` data has `r ncol(instacart)` variables and `r nrow(instacart)` observations. The variables include `r names(instacart)`. Among these, eval_set, product_name, aisle, and department are character variables, and the others are numerical variables. 

### How many aisles are there, and which aisles are the most items ordered from?

```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs))
```

There are `134` aisles. The most items ordered form the `fresh vegetables` aisle, and the number of orders from this aisle is 150609. 

### Plotting the number of items ordered in each aisle with more than 10000 items ordered. 

```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  arrange(desc(n_obs)) %>% 
  filter(n_obs > 10000) %>% 
  ggplot(aes(x = aisle, y = n_obs)) +
  geom_point() +
  labs(
    title = "The Number of Items Ordered in Each Aisle", 
    x = "Aisles", 
    y = "The number of items ordered"
  ) + 
  theme(axis.text.x = element_text(angle = 50, hjust = 1))
```

The scatter plot shows the number of items order in each aisle, which these aisles are those has more than 10000 items ordered. 

### The three most popular items in “baking ingredients”, “dog food care”, and “packaged vegetables fruits”

```{r}
baking = instacart %>% 
  filter(aisle %in% "baking ingredients") %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  arrange(desc(n)) %>% 
  filter(rank <= 3) 

dog = instacart %>% 
  filter(aisle %in% "dog food care") %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  arrange(desc(n)) %>% 
  filter(rank <= 3) 

veg = instacart %>% 
  filter(aisle %in% "packaged vegetables fruits") %>% 
  group_by(aisle) %>%
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  arrange(desc(n)) %>% 
  filter(rank <= 3) 

Q3 = bind_rows(baking, dog, veg) %>% 
  subset(select = -rank) %>% 
  knitr::kable()
```

The table shows that for `baking ingredients`, the top three popular items are `light brown sugar`, `pure baking soda`, and `cane sugar`, and the corresponding times of order are 499, 387, and 336; for `dog food care` aisle, the top three popular items are `Snack Sticks Chicken & Rice Recipe Dog Treats`, `Organix Chicken & Brown Rice Recipe`, and `Small Dog Biscuits`, and the corresponding times of order are 30, 28, and 26; for `packaged vegetables fruits` aisle, the top three popular items are `organic baby spinach`, `organic raspberries`, and `organic blueberries`, and their corresponding times of order are 9784, 5546, and 4966. 

### The mean hour at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week

```{r}
Q4 = 
  instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_order_hour = mean(order_hour_of_day)) %>% 
  mutate(order_dow = recode(order_dow, `0` = "Sunday", `1` = "Monday", `2` = "Tuesday", `3` = "Wednesday", `4` = "Thurday", `5` = "Friday", `6` = "Saturday")) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_order_hour
  ) %>% 
  knitr::kable()
```

The table shows that 


